### 2020-10-16 2020/WCGO_MCO_OptimizationLetters/2020_WCGO_MCO.tex
sorted the list of references

The initial theoretical analysis of global search properties when using search information was performed in \cite{c48}. The obtained theoretical statements can be reformulated as applied to lexicographic multicriteria optimization problems.

@@

\bibitem{c1} Miettinen K.: Nonlinear Multiobjective Optimization. Springer. (1999)
\bibitem{c2} Ehrgott, M.: Multicriteria Optimization. Springer. (2nd ed., 2010)
\bibitem{c3} Collette, Y., Siarry, P.: Multiobjective Optimization: Principles and Case Studies (Decision Engineering). Springer. (2011)
\bibitem{c4} Marler, R.T., Arora, J.S.: Multi-Objective Optimization: Concepts and Methods for Engineering. VDM Verlag. (2009)
\bibitem{c5} Pardalos, P.M., {\v Z}ilinskas, A., {\v Z}ilinskas, J.: Non-Convex Multi-Objective Optimization. Springer. (2017)
\bibitem{c6} Marler, R., Arora , J.: Survey of multi-objective optimization methods for engineering. Struct. Multidisc. Optim. \textbf{26}, 369--395 (2004)
\bibitem{c7} Figueira,J., Greco, S., Ehrgott, M., (eds.): Multiple criteria decision analysis: State of the art surveys. Springer, New York (NY). (2005)
\bibitem{c8} Zavadskas, E.K., Turskis, Z., Kildien\.e, S.: State of art surveys of overviews on MCDM/MADM methods. Technol. Econ. Dev. Econ. \textbf{20}, 165--179 (2014)
\bibitem{c9} Hillermeier, C., Jahn, J.: Multiobjective optimization: survey of methods and industrial applications. Surv. Math. Ind. \textbf{11}, 1--42 (2005)
\bibitem{c10} Branke, J., Deb, K., Miettinen, K., Slowinski, R., (eds.): Multi-Objective Optimization--Interactive and Evolutionary Approaches. Springer, Berlin. (2008)
\bibitem{c11} Deb, K.: Multi-Objective Optimization using Evolutionary Algorithms. Wiley, Chichester. (2001)
\bibitem{c12} Yang, X.-S.: Nature-inspired Metaheuristic Algorithms. Luniver Press, Frome. (2008) 
\bibitem{c13} Tan, K.C., Khor, E.F., Lee, T.H.: Multi-objective Evolutionary Algorithms and Applications. Springer-Verlag, London. (2005)
\bibitem{c14} Eichfelder, G.: Scalarizations for adaptively solving multi-objective optimization problems. Comput. Optim. Appl. \textbf{44}, 249--273 (2009)
\bibitem{c15} Jones, D.R.: A taxonomy of global optimization methods based on response surfaces. J. Glob. Optim. \textbf{21}, 345--383 (2001)
\bibitem{c16} Voutchkov, I., Keane, A.: Multi-objective optimization using surrogates. Comput. Intell. Optim. Adapt. Learn. Optim. \textbf{7}, 155--175 (2010)
\bibitem{c17} Strongin, R.G.: Numerical Methods in Multiextremal Problems: Information-statistical Algorithms. Nauka, Moscow. (1978, in Russian) 
\bibitem{c18} Strongin, R.G., Sergeyev, Y.D.: Global optimization with non-convex constraints. Sequential and parallel algorithms. Kluwer Academic Publishers, Dordrecht. (2nd ed. 2013, 3rd ed. 2014).
\bibitem{c19} T\"orn, A., {\v Z}ilinskas, A.: Global Optimization. Lecture Notes in Computer Science, 350. Springer-Verlag, Berlin. (1989)
\bibitem{c20} Horst, R., Tuy, H.: Global Optimization: Deterministic Approaches. Springer-Verlag, Berlin. (1990)
\bibitem{c21} Zhigljavsky, A.A.: Theory of Global Random Search. Kluwer Academic Publishers, Dordrecht. (1991)
\bibitem{c22} Pint\'er, J.D.: Global Optimization in Action (Continuous and Lipschitz Optimization: Algorithms, Implementations and Applications). Kluwer Academic Publishers, Dortrecht. (1996)
\bibitem{c23} Sergeyev, Y.D., Strongin, R.G., Lera, D.: Introduction to Global Optimization Exploiting Space-filling Curves. Springer. (2013)
\bibitem{c24} Locatelli, M., Schoen, F.: Global Optimization: Theory, Algorithms, and Applications. SIAM. (2013)
\bibitem{c25} Floudas, C.A., Pardalos, M.P.: Recent Advances in Global Optimization. Princeton University Press. (2016)
\bibitem{c26} Lera, D., Sergeyev, Y.D.: Deterministic global optimization using space-filling curves and multiple estimates of Lipschitz and Holder constants. Commun. Nonlinear Sci. \textbf{23}(1-3), 328--342 (2015)
\bibitem{c27} Gergel, V.: A unified approach to use of coprocessors of various types for solving global optimization problems. 2nd Int. Conf. on MACSI. 13--18 (2015). DOI: 10.1109/MCSI.2015.18
\bibitem{c28} Arora, R.K.: Optimization: Algorithms and Applications. CRC Press. (2015)
\bibitem{c29} Bazaraa, M.S., Sherali, H.D., Shetty, C.M.: Nonlinear Programming: Theory and Algorithms. John Wiley and Sons. (2006)
\bibitem{c30} Gergel, V.P., Kozinov, E.A.: Accelerating multicriterial optimization by the intensive exploitation of accumulated search data. In: 	AIP Conf. Proc., \textbf{1776}, 090003 (2016). DOI: 10.1063/1.4965367
\bibitem{c31} Gergel, V.P., Kozinov, E.A.: Efficient multicriterial optimization based on intensive reuse of search information.  J. Glob. Optim. \textbf{71}(1), 73--90 (2018). DOI: 10.1007/s10898-018-0624-3
\bibitem{c32} Sysoyev, A., Barkalov, K., Gergel, V.: Globalizer: A novel supercomputer software system for solving time-consuming global optimization problems. Numer. Algebra, Control. Optim. \textbf{8}(1), 47--62 (2018)
\bibitem{c33} Kvasov, D.E., Sergeyev, Y.D.: Deterministic approaches for solving practical black-box global optimization problems. Adv. Eng. Softw. \textbf{80}, 58--66 (2015)
\bibitem{c34} Modorskii, V., Gaynutdinova, D., Gergel, V., Barkalov, K.: Optimization in design of scientfic products for purposes of cavitation problems. AIP Conf. Proc. \textbf{1738}, 400013 (2016)
\bibitem{c35} Evtushenko, Yu.G., Posypkin, M.A.: A deterministic algorithm for global multi-objective optimization. Optim. Methods Softw., \textbf{29}(5), 1005--1019 (2014)
\bibitem{c36} {\v Z}ilinskas, A., {\v Z}ilinskas, J.: Adaptation of a one-step worst-case optimal univariate algorithm of bi-objective Lipschitz optimization to multidimensional problems. Commun. Nonlinear Sci. Numer. Simul., \textbf{21}(1-3), 89--98 (2015)

\bibitem{c38} Zarepisheh, M., Khorram, E.: On the transformation of lexicographic nonlinear multiobjective  programs to single objective programs. Math. Methods Oper. Res. \textbf{74}, 217--231 (2011)
\bibitem{c39} Haimes, Y.Y., Lasdon, L., Wismer, D.: On a bicriterion formulation of the problem of integrated systems identification and system optimization. IEEE Trans. Syst. Man Cybern. \textbf{1}, 296--297 (1971)
\bibitem{c40} Chankong, V., Haimes, Y.Y.: Multiobjective Decision Making: Theory and Methodology. North-Holland Series in System Science and Engineering. New York (NY): Elsevier. (1983)
\bibitem{c41} Ehrgott, M., Ruzika, S.: Improved $\varepsilon$-constraint method for multiobjective programming. J. Optim. Theory Appl. \textbf{138}, 375--396 (2008)
\bibitem{c42} Rastegar, N., Khorram, E.: Relaxation of constraints in lexicographic multiobjective programming problems. A Journal of Mathematical Programming and Operations Research, \textbf{64}, 2111--2129 (2015)
\bibitem{c43} Castro-Gutierrez, J., Landa-Silva, D., P\'erez, J.M.: Improved dynamic lexicographic ordering for multi-objective optimisation. Lect. Notes Comput. Sci., \textbf{6239}, 31--40 (2010) 
\bibitem{c44} Audet, C., Savard, G., Zghal, W.: Multiobjective optimization through a series of single-objective formulations. SIAM J. Optim. \textbf{19}(1), 188--210 (2008)
\bibitem{c45} Sergeyev, Y.D., Kvasov, D.E.: Deterministic Global Optimization: An Introduction to the Diagonal Approach (Springer Briefs in Optimization). Springer. (2017)
\bibitem{c46} Carr, C.R., Howe, C.W.: Quantitative Decision Procedures in Management and Economic: Deterministic Theory and Applications. New York: McGraw–Hill (1964)
\bibitem{c47} Dam, E.R., Husslage, B., Hertog, D.: One-dimensional nested maximin designs. J. Glob. Optim. \textbf{46}(2), 287--306 (2010)
\bibitem{c48} Gergel, V., Kozinov, E.: Efficient multicriterial optimization based on intensive reuse of search information, J. Glob. Optim., \textbf{71}(1), 73--90 (2018). DOI:10.1007/s10898-018-0624-3.
\bibitem{c49} Mart\'l, L., Garc\'la, J., Berlanga, A., Molina, J.M.: A stopping criterion for multi-objective optimization evolutionary algorithms. Inf. Sci. \textbf{367--368}, 700--718 (2016)
\bibitem{c50} Dilettoso, E., Rizzo, S.A., Salerno, N.: A weakly Pareto compliant quality indicator. Math. Comput. Appl. \textbf{22}(1), 25 (2017)
\bibitem{c51} Wu, J., Azarm, S.: Metrics for quality assessment of a multiobjective design optimization solution set. J. Mech. Des. \textbf{123}(1), 18--25 (2001)
\bibitem{c52} Audet, C., Bigeon, J., Cartier, D., Le Digabel, S., Salomon, L.: Performance indicators in multiobjective optimization. Technical Report G-2018-90, Les cahiers du GERAD. (2018)
\bibitem{c53} Huband, S., Hingston, P., Barone, L., While, L.: A review of multiobjective test problems and a scalable test problem toolkit. IEEE T. Evolut. Comput. \textbf{10}(5), 477--506 (2006)
\bibitem{c54} Hansen, N., Auger, A., Finck, S., Ros, R.: Real-Parameter Black-Box Optimization Benchmarking 2009: Experimental Setup. INRIA Research Report RR-6829, INRIA Saclay-Ile-de-France. updated February 2010 (2009)
\bibitem{c55} Cust\'odio, A.L., Madeira, J.F.A., Vaz, A.I.F., Vicente, L.N.: Direct multisearch for multiobjective optimization. SIAM J. Optim. \textbf{21}(3), 1109--1140 (2011)
\bibitem{c56} Brockhoff, D., Tusar, T., Auger, A., Hansen, N.: Using well-understood single-objective functions in multiobjective black-box optimization test suites. (2019) https://arxiv.org/abs/1604.00359 
\bibitem{c57} Cococcioni, M., Cudazzo, A., Pappalardo, M., Sergeyev, Y.D.: Solving the lexicographic multi-objective mixed-integer linear programming problem using branch-and-bound and grossone methodology. Commun. Nonlinear Sci. Numer. Simul. \textbf{84}, 105177 (2020)
\bibitem{c58} Cococcioni, M., Pappalardo, M., Sergeyev, Y.D.: Lexicographic multi-objective linear programming using grossone methodology: Theory and algorithm. Appl. Math. Comput. \textbf{318}, 298--311 (2018)
\bibitem{c59} Lai, L., Fiaschi, L., Cococcioni, M.: Solving mixed Pareto-lexicographic multi-objective optimization problems: the case of priority chains. Swarm Evol. Comput. \textbf{55}, 100687 (2020) DOI: 10.1016/j.swevo.2020.100687

\bibitem{Book2013} Strongin, R.G., Gergel, V.P., Grishagin, V.A., Barkalov, K.A.: Parallel computing in global optimization problems. MSU Press, Moscow. (2013, in Russian)

\bibitem{Sergeyev2003} Sergeyev, Y.D., Pugliese, P., Famularo, D.: Index information algorithm with local tuning for solving multidimensional global optimization problems with multiextremal constraints. Math. Program., Ser. A \textbf{96}, 489--512 (2003)

@@

\bibitem{Grishagin2019} Gergel V.P., Grishagin V.A., Israfilov R.A. Adaptive dimensionality reduction in multiobjective optimization with multiextremal criteria. Lecture Notes in Computer Science, \textbf{11331}, 129--140 (2019)

>>>>

The initial theoretical analysis of global search properties when using search information was performed in \cite{c31}. The obtained theoretical statements can be reformulated as applied to lexicographic multicriteria optimization problems.

@@

\bibitem{c1} Miettinen K.: Nonlinear Multiobjective Optimization. Springer. (1999)
\bibitem{c2} Ehrgott, M.: Multicriteria Optimization. Springer. (2nd ed., 2010)
\bibitem{c3} Collette, Y., Siarry, P.: Multiobjective Optimization: Principles and Case Studies (Decision Engineering). Springer. (2011)
\bibitem{c4} Marler, R.T., Arora, J.S.: Multi-Objective Optimization: Concepts and Methods for Engineering. VDM Verlag. (2009)
\bibitem{c5} Pardalos, P.M., {\v Z}ilinskas, A., {\v Z}ilinskas, J.: Non-Convex Multi-Objective Optimization. Springer. (2017)
\bibitem{c6} Marler, R., Arora , J.: Survey of multi-objective optimization methods for engineering. Struct. Multidisc. Optim. \textbf{26}, 369--395 (2004)
\bibitem{c7} Figueira,J., Greco, S., Ehrgott, M., (eds.): Multiple criteria decision analysis: State of the art surveys. Springer, New York (NY). (2005)
\bibitem{c8} Zavadskas, E.K., Turskis, Z., Kildien\.e, S.: State of art surveys of overviews on MCDM/MADM methods. Technol. Econ. Dev. Econ. \textbf{20}, 165--179 (2014)
\bibitem{c9} Hillermeier, C., Jahn, J.: Multiobjective optimization: survey of methods and industrial applications. Surv. Math. Ind. \textbf{11}, 1--42 (2005)
\bibitem{c14} Eichfelder, G.: Scalarizations for adaptively solving multi-objective optimization problems. Comput. Optim. Appl. \textbf{44}, 249--273 (2009)
\bibitem{c10} Branke, J., Deb, K., Miettinen, K., Slowinski, R., (eds.): Multi-Objective Optimization--Interactive and Evolutionary Approaches. Springer, Berlin. (2008)
\bibitem{c11} Deb, K.: Multi-Objective Optimization using Evolutionary Algorithms. Wiley, Chichester. (2001)
\bibitem{c12} Yang, X.-S.: Nature-inspired Metaheuristic Algorithms. Luniver Press, Frome. (2008) 
\bibitem{c13} Tan, K.C., Khor, E.F., Lee, T.H.: Multi-objective Evolutionary Algorithms and Applications. Springer-Verlag, London. (2005)

\bibitem{c57} Cococcioni, M., Cudazzo, A., Pappalardo, M., Sergeyev, Y.D.: Solving the lexicographic multi-objective mixed-integer linear programming problem using branch-and-bound and grossone methodology. Commun. Nonlinear Sci. Numer. Simul. \textbf{84}, 105177 (2020)
\bibitem{c58} Cococcioni, M., Pappalardo, M., Sergeyev, Y.D.: Lexicographic multi-objective linear programming using grossone methodology: Theory and algorithm. Appl. Math. Comput. \textbf{318}, 298--311 (2018)
\bibitem{c59} Lai, L., Fiaschi, L., Cococcioni, M.: Solving mixed Pareto-lexicographic multi-objective optimization problems: the case of priority chains. Swarm Evol. Comput. \textbf{55}, 100687 (2020) DOI: 10.1016/j.swevo.2020.100687

\bibitem{c38} Zarepisheh, M., Khorram, E.: On the transformation of lexicographic nonlinear multiobjective  programs to single objective programs. Math. Methods Oper. Res. \textbf{74}, 217--231 (2011)
\bibitem{c39} Haimes, Y.Y., Lasdon, L., Wismer, D.: On a bicriterion formulation of the problem of integrated systems identification and system optimization. IEEE Trans. Syst. Man Cybern. \textbf{1}, 296--297 (1971)
\bibitem{c40} Chankong, V., Haimes, Y.Y.: Multiobjective Decision Making: Theory and Methodology. North-Holland Series in System Science and Engineering. New York (NY): Elsevier. (1983)
\bibitem{c41} Ehrgott, M., Ruzika, S.: Improved $\varepsilon$-constraint method for multiobjective programming. J. Optim. Theory Appl. \textbf{138}, 375--396 (2008)

\bibitem{c42} Rastegar, N., Khorram, E.: Relaxation of constraints in lexicographic multiobjective programming problems. A Journal of Mathematical Programming and Operations Research, \textbf{64}, 2111--2129 (2015)
\bibitem{c43} Castro-Gutierrez, J., Landa-Silva, D., P\'erez, J.M.: Improved dynamic lexicographic ordering for multi-objective optimisation. Lect. Notes Comput. Sci., \textbf{6239}, 31--40 (2010)

\bibitem{c31} Gergel, V.P., Kozinov, E.A.: Efficient multicriterial optimization based on intensive reuse of search information.  J. Glob. Optim. \textbf{71}(1), 73--90 (2018). DOI: 10.1007/s10898-018-0624-3
\bibitem{c44} Audet, C., Savard, G., Zghal, W.: Multiobjective optimization through a series of single-objective formulations. SIAM J. Optim. \textbf{19}(1), 188--210 (2008)

\bibitem{c15} Jones, D.R.: A taxonomy of global optimization methods based on response surfaces. J. Glob. Optim. \textbf{21}, 345--383 (2001)
\bibitem{c16} Voutchkov, I., Keane, A.: Multi-objective optimization using surrogates. Comput. Intell. Optim. Adapt. Learn. Optim. \textbf{7}, 155--175 (2010)
\bibitem{c17} Strongin, R.G.: Numerical Methods in Multiextremal Problems: Information-statistical Algorithms. Nauka, Moscow. (1978, in Russian)

\bibitem{c18} Strongin, R.G., Sergeyev, Y.D.: Global optimization with non-convex constraints. Sequential and parallel algorithms. Kluwer Academic Publishers, Dordrecht. (2nd ed. 2013, 3rd ed. 2014).
\bibitem{c19} T\"orn, A., {\v Z}ilinskas, A.: Global Optimization. Lecture Notes in Computer Science, 350. Springer-Verlag, Berlin. (1989)
\bibitem{c20} Horst, R., Tuy, H.: Global Optimization: Deterministic Approaches. Springer-Verlag, Berlin. (1990)
\bibitem{c21} Zhigljavsky, A.A.: Theory of Global Random Search. Kluwer Academic Publishers, Dordrecht. (1991)
\bibitem{c22} Pint\'er, J.D.: Global Optimization in Action (Continuous and Lipschitz Optimization: Algorithms, Implementations and Applications). Kluwer Academic Publishers, Dortrecht. (1996)
\bibitem{c23} Sergeyev, Y.D., Strongin, R.G., Lera, D.: Introduction to Global Optimization Exploiting Space-filling Curves. Springer. (2013)
\bibitem{c24} Locatelli, M., Schoen, F.: Global Optimization: Theory, Algorithms, and Applications. SIAM. (2013)
\bibitem{c25} Floudas, C.A., Pardalos, M.P.: Recent Advances in Global Optimization. Princeton University Press. (2016)

\bibitem{c45} Sergeyev, Y.D., Kvasov, D.E.: Deterministic Global Optimization: An Introduction to the Diagonal Approach (Springer Briefs in Optimization). Springer. (2017)
\bibitem{c46} Carr, C.R., Howe, C.W.: Quantitative Decision Procedures in Management and Economic: Deterministic Theory and Applications. New York: McGraw–Hill (1964)
\bibitem{c47} Dam, E.R., Husslage, B., Hertog, D.: One-dimensional nested maximin designs. J. Glob. Optim. \textbf{46}(2), 287--306 (2010)
\bibitem{Grishagin2019} Gergel V.P., Grishagin V.A., Israfilov R.A. Adaptive dimensionality reduction in multiobjective optimization with multiextremal criteria. Lecture Notes in Computer Science, \textbf{11331}, 129--140 (2019)

@@

\bibitem{c26} Lera, D., Sergeyev, Y.D.: Deterministic global optimization using space-filling curves and multiple estimates of Lipschitz and Holder constants. Commun. Nonlinear Sci. \textbf{23}(1-3), 328--342 (2015)
\bibitem{c27} Gergel, V.: A unified approach to use of coprocessors of various types for solving global optimization problems. 2nd Int. Conf. on MACSI. 13--18 (2015). DOI: 10.1109/MCSI.2015.18
\bibitem{c28} Arora, R.K.: Optimization: Algorithms and Applications. CRC Press. (2015)
\bibitem{c29} Bazaraa, M.S., Sherali, H.D., Shetty, C.M.: Nonlinear Programming: Theory and Algorithms. John Wiley and Sons. (2006)

\bibitem{Book2013} Strongin, R.G., Gergel, V.P., Grishagin, V.A., Barkalov, K.A.: Parallel computing in global optimization problems. MSU Press, Moscow. (2013, in Russian)
\bibitem{Sergeyev2003} Sergeyev, Y.D., Pugliese, P., Famularo, D.: Index information algorithm with local tuning for solving multidimensional global optimization problems with multiextremal constraints. Math. Program., Ser. A \textbf{96}, 489--512 (2003)

\bibitem{c30} Gergel, V.P., Kozinov, E.A.: Accelerating multicriterial optimization by the intensive exploitation of accumulated search data. In: 	AIP Conf. Proc., \textbf{1776}, 090003 (2016). DOI: 10.1063/1.4965367
\bibitem{c32} Sysoyev, A., Barkalov, K., Gergel, V.: Globalizer: A novel supercomputer software system for solving time-consuming global optimization problems. Numer. Algebra, Control. Optim. \textbf{8}(1), 47--62 (2018)

\bibitem{c49} Mart\'l, L., Garc\'la, J., Berlanga, A., Molina, J.M.: A stopping criterion for multi-objective optimization evolutionary algorithms. Inf. Sci. \textbf{367--368}, 700--718 (2016)
\bibitem{c50} Dilettoso, E., Rizzo, S.A., Salerno, N.: A weakly Pareto compliant quality indicator. Math. Comput. Appl. \textbf{22}(1), 25 (2017)
\bibitem{c51} Wu, J., Azarm, S.: Metrics for quality assessment of a multiobjective design optimization solution set. J. Mech. Des. \textbf{123}(1), 18--25 (2001)
\bibitem{c52} Audet, C., Bigeon, J., Cartier, D., Le Digabel, S., Salomon, L.: Performance indicators in multiobjective optimization. Technical Report G-2018-90, Les cahiers du GERAD. (2018)
\bibitem{c35} Evtushenko, Yu.G., Posypkin, M.A.: A deterministic algorithm for global multi-objective optimization. Optim. Methods Softw., \textbf{29}(5), 1005--1019 (2014)
\bibitem{c36} {\v Z}ilinskas, A., {\v Z}ilinskas, J.: Adaptation of a one-step worst-case optimal univariate algorithm of bi-objective Lipschitz optimization to multidimensional problems. Commun. Nonlinear Sci. Numer. Simul., \textbf{21}(1-3), 89--98 (2015)

\bibitem{c53} Huband, S., Hingston, P., Barone, L., While, L.: A review of multiobjective test problems and a scalable test problem toolkit. IEEE T. Evolut. Comput. \textbf{10}(5), 477--506 (2006)
\bibitem{c54} Hansen, N., Auger, A., Finck, S., Ros, R.: Real-Parameter Black-Box Optimization Benchmarking 2009: Experimental Setup. INRIA Research Report RR-6829, INRIA Saclay-Ile-de-France. updated February 2010 (2009)
\bibitem{c55} Cust\'odio, A.L., Madeira, J.F.A., Vaz, A.I.F., Vicente, L.N.: Direct multisearch for multiobjective optimization. SIAM J. Optim. \textbf{21}(3), 1109--1140 (2011)
\bibitem{c56} Brockhoff, D., Tusar, T., Auger, A., Hansen, N.: Using well-understood single-objective functions in multiobjective black-box optimization test suites. (2019) https://arxiv.org/abs/1604.00359

\bibitem{c33} Kvasov, D.E., Sergeyev, Y.D.: Deterministic approaches for solving practical black-box global optimization problems. Adv. Eng. Softw. \textbf{80}, 58--66 (2015)
\bibitem{c34} Modorskii, V., Gaynutdinova, D., Gergel, V., Barkalov, K.: Optimization in design of scientfic products for purposes of cavitation problems. AIP Conf. Proc. \textbf{1738}, 400013 (2016)
